\documentclass{letter}
\usepackage[paperwidth=6in,paperheight=9in]{geometry}
\setlength{\parindent}{20pt}

\begin{document}

\noindent
{ \center \textbf {PREFACE \\
to \\
Echoes of Grace Hymn Book \\
} }


Echoes of Grace Hymn Book is basically a revision of the Messages of Love Hymn Book, which the Lord has graciously used for blessing in Sunday school and gospel work, as well as in the homes of the saints, for more than forty years.

The new title has been adopted to prevent confusion from the fact that in the new book most hymns from the old book appear under different numbers.

The editors have sought to satisfy the widely expressed desire for a more ample selection of evangelical and children's hymns. More than sixty gospel gospel hymns of proved merit, along with twenty-five more for Christians, have been added, while the hymns for children contain thirty-seven additional pieces. For more convenient reference, the gospel hymns have been placed in the front of the book, those for Christians in the center, and those for children toward the end.

In order to accommodate so much new material, it has been necessary to exclude a few little-used hymns from the old book. In this matter the cooperation of brethren in different sections was obtained in the desire to avoid eliminating hymns that are in general use.

The tunes have been chosen with considerable research and consultation, with due deference to prevailing standards of musical taste. Where words and music have become firmly wedded, despite a defectiveness of the latter, the old tune has been retained. In many other cases an improved tune has been set, and will, it is hoped, encourage more frequent use of the hymn.

A sincere effort has been made to trace possible copyrights. The publishers ask forbearance in the case of any inadvertent infringement, and will gladly rectify the same in a future printing.

A work undertaken in the consciousness of human insufficiency, but with confidence in the Lord's enabling grace for every task, is thus committed to Him for His gracious blessing, and in His service to the dear saints at large.

\noindent
April 1951.

\end{document}

